---
title: "DSassignment_ggplot"
author: "Judy Ban"
date: "February 15, 2018"
output: html_document
---
#load packages
```{r}
library(tidyverse)
library(phyloseq)
```

#load Saanich.metadata.txt

```{r}
metadata = read.table (file="Saanich.metadata.txt", header=TRUE, row.names=1, sep="\t", na.strings=c("NAN","NA","."))
```


#Exercise 1  
plot the points with NO2_uM values on the x-axis and Depth_m values on the y-axis  
```{r}
ggplot(metadata, aes(x=NO2_uM, y=Depth_m)) +
  geom_point()
```

Change points into purple and triangles  

```{r}
ggplot(metadata, aes(x=NO2_uM, y=Depth_m)) +
  geom_point(color="purple", pch=17)
```

#Exercise 2  
changing temperature from celsius to fehrenheit, then plotting the temperature in F on the x axis and Depth_m on the Y axis  


```{r}
metadata %>% 
  mutate(Temperature_F = Temperature_C*1.8+32) %>% 
  ggplot(aes(x=Temperature_F, y=Depth_m)) +
  geom_point() 
```
 
  
#Exercise 3  
load physeq  
```{r}
load("phyloseq_object.RData")
```


physeq  

Transform absolute abundance into percent abundance  

```{r}
physeq_percent = transform_sample_counts(physeq, function(x) 100 * x/sum(x))  
```


Plotting the genus level communities by depth with respect to percent abundance  
```{r}
plot_bar(physeq_percent, fill="Genus")  
```


Removing the black lines on the bars, and making the lables of the axis as well as the title more descriptive  

```{r}
plot_bar(physeq_percent, fill="Genus") + 
  geom_bar(aes(fill=Genus), stat="identity") + labs( x = "Sample depth", y = "Percent relative abundance",
                                                       title ="Genus from 10 to 200 m in Saanich Inlet")  
```

                                                       
#Exercise 4  
Manipulating the metadata so that the nutrients of interest, H4_uM,NO2_uM,NO3_uM,O2_uM,PO4_uM,SiO2_uM, are all in one variable. Turn the table into an object called "gather".The column with the nutrient information is named "nutrients" and the column with values corresponding the the nutrients is called "uM". Then plorring the graphs with lines and points. 

```{r}
metadata %>%
  gather(nutrients, uM, NH4_uM,NO2_uM,NO3_uM,O2_uM,PO4_uM,SiO2_uM) %>%  
  ggplot(fill="nutrients") +
  geom_line(aes(x=Depth_m, y=uM), stat="identity") + 
  geom_point(aes(x=Depth_m, y=uM), stat="identity") +
  facet_wrap(~nutrients, scales="free_y") +
  theme(legend.position="none")
  
```


